Stable Hot Spot Analysis (Draft)

### 2017-06-15 paper-main.tex
Updated aggregation and blur

Our results are based on the cab taxi dataset from New York, Manhattan \cite{TODO}. 
We used only the dataset of January 2016. From that
dataset we used the $pickup\_longitude$ and $pickup\_latitude$ column. 
The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
Aggregation size 1 means we aggregate every point, which was in range of $100x100 \cdot 0.000001$ into one pixel. 
For aggregation size Z we aggregated ZxZ pixel from aggregated size 1 into a new pixel.
%
For our measurements we specified the following data series:
\begin{itemize}
 \item $W_i$: The weight matrix W is from 3 to 47 with a stepsize of 4.
 \item $F_j$: The focal matrix F is from  17 to 137 with a stepsize of 12. F is ignored for $G^*$ but not for Focal $G^*$
 \item $R_z$: The aggregation level is from 1 to 6 with a stepsize of 1. R represents the raster
\end{itemize}
\begin{definition}
The SoH for a singled evalution run in the weight dimension is defined as:
\begin{displaymath}
\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i+2}, st, F_{j}) ) 
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i+2}, st, F_{j}) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
\end{displaymath}
The SoH for a singled evalution run in the focal dimension is defined as:
\begin{displaymath}
\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i}, st, F_{j+1}) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i}, st, F_{j+1}) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
\end{displaymath}
The SoH for a singled evalution run in the aggregation dimension is defined as:
\begin{displaymath}
\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_{z+1}, W_{i}, st, F_{j}) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_{z+1}, W_{i}, st, F_{j}) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
\end{displaymath}

@@

The results can be found in figure ~\ref{fig:Zoom}.
For the upward property, $G^*$ is always better than Focal $G^*$, compared to the results from figure
\ref{fig:SoHZoom}. Focal $G^*$ reaches the same result as $G^*$ at zoom level 5 .
For the downward property, Focal $G^*$ leads to better results at zoom level 5.

@@

Blur is a slice plane through our three dimensional space. 
W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
\begin{definition} Blur run:
\begin{displaymath}
\SOHUP( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
\end{displaymath}
\begin{displaymath}
z =3, i \in [1,6],dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}
The blur results are plotted in Fig.~\ref{fig:Blur}.
The slice plane of the weight dimension is consistent with figure ~\ref{fig:SoHWeight}.
Higher weight leads in general to better results for Focal $G^*$. 
$G^*$ doesn't fit to the mean of our whiskerplot.

>>>>

Our results are based on the cab taxi dataset from New York, Manhattan \cite{TODO}. 
We used only the dataset of January 2016. From that
dataset we used the $pickup\_longitude$ and $pickup\_latitude$ column. 
The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
Aggregation size 1 means we aggregate every point, which was in range of $100x100 \cdot 0.000001$ into one pixel. 
For aggregation size Z we aggregated ZxZ pixel from aggregated size 1 into a new pixel.
%
For our measurements we specified the following data series:
\begin{itemize}
 \item $W_i$: The weight matrix W is from 3 to 47 with a stepsize of 4.
 \item $F_j$: The focal matrix F is from  17 to 137 with a stepsize of 12. F is ignored for $G^*$ but not for Focal $G^*$
 \item $R_z$: The aggregation level is from 1 to 6 with a stepsize of 1. R represents the raster
\end{itemize}
\begin{definition}
The SoH for a singled evalution run in the weight dimension is defined as:
\begin{displaymath}
\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) ) 
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
\end{displaymath}

The SoH for a singled evalution run in the focal dimension is defined as:
\begin{displaymath}
\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
\end{displaymath}

The SoH for a singled evalution run in the aggregation dimension is defined as:
\begin{displaymath}
\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}

@@

The results can be found in Fig.~\ref{fig:Zoom}.
For the upward property, $G^*$ is better than Focal $G^*$ in most cases, compared to the results from figure
\ref{fig:SoHZoom}. At aggregation level 5 $G^*$ is worse than Focal $G^*$, but at this point $G^*$ was extrem 
good if you compare it to the whiskerplot in Fig.~\ref{fig:zUp}.
For \SOHDOWN $G^*$ has its peak for aggregation level 5, which is consistent with Fig.~\ref{fig:zDown}.
The result in Fig.~\ref{fig:Zoom} where consitent that $G^*$ is always better than Focal $G^*$ but suprisingly 
we found an outlier.

@@

Blur is a slice plane through our three dimensional space. 
W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
\begin{definition} Blur run:
\begin{displaymath}
\SOHUP( G^*(R_z, W_{7+(i-1) \cdot 2}, st, F), G^*(R_{z}, W_{7+i \cdot 2}, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_{7+(i-1) \cdot 2}, st, F), G^*(R_{z}, W_{7+i \cdot 2}, st, F) )
\end{displaymath}
\begin{displaymath}
z =3, i \in [1,6],dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}
The blur results are plotted in Fig.~\ref{fig:Blur}.
In this slice one can see that $G^*$ leads to better results compared to Focal $G^*$ for \SOHDOWN. 
This is because focal size F is set
to 41x41. We saw that a higher focal size leads to better results. We saw in Fig.~\ref{images/whiskerPlot/wDown}
that an increas of the weight leads to better results. This slice plane is not consistent. Focal $G^*$ is even decreasing.
For the \SOHUP Focal $G^*$ compared to $G^*$ is equal good if the points are counted. But $G^*$ has a poor performance with the smallest 
weights. Foal $G^*$ is mostly above 0.4.
